Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-07-12 manuscript/manuscript.tex
Started writing Theory -> Analytical Solutions

>>>>

\subsection{Analytical Solutions for Spherical Shell}

In order to test the accuracy of the GLQ approximation, \citet{Uieda2016} compared the computed gravity fields with the ones generated by a spherical shell, the exceptional case with analytical solution \citep{Misuska2006,}.

In case of variable density tesseroids, the comparison must obviously be made with a variable density spherical shell, whose analytical solution will depend on the chosen density function.
Moreover, the literature does not develop the analytical solution
